%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------
    \cventry
    {Software Engineer} % Job title
    {Proactis Holdings Ltd / Perfect Commerce} % Organization
    {Newport News, VA} % Location
    {March '13 til August '15,\newline February '17 til November '21} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Current responsibility is to maintain two multitenant SaaS applications by adding features, fixing bugs, and addressing technical debt.
            The main application is a Java application that uses a combination of JSPs and TypeScript angular. This application has an Oracle database.
            The other application is a C\#/.NET application that uses WebForms, vanilla JavaScript, jQuery, and CSS with an Oracle database.}
        \item {Over my career at Proactis, I led development of three different products(not all at once). 
            While I was a lead, I worked with closesly with Product Management and implementation specialists to design new features 
            and help guide the development teams on the best way to fit them into the products.}
        \item {Worked to make an Internet Explorer focused C\#/.NET Website fully functional in other more modern browsers while adding features and fixing bugs.}
        \item {Worked with the IT Ops team to automate the C\#/.NET Website's build and deployment process.
            This was a manual process with multiple steps to it. Remove the manual steps and some minor tweaks cut the runtime in half.} 
        \item {Rewrote a portion of the C\#/.NET application that exported RFXs to word documents using the Word 2003 interop and produced a .doc file. 
            It was rewritten using .NET Core and the Microsoft OpenXml SDK to produce a .docx file.}
        \item {Worked to migrate another application's build and deployment process from being configured 
            through the Jenkins UI to a scripted pipeline stored in git.}
        \item {Worked with the development team to design and implement a reporting database and an adhoc reporting solution built with JasperReports.
            Worked to create an ETL and CDC process to move data from the live databases to the reporting databases.}
        \item {Worked on refactoring our PCI application written in Go so that we were able to have a successful PCI audit.
            The public and private procurement applications used this application to store the credit card data on orders that used them.}
        %\item {Worked with the DBA team to upgrade the oracle database from 11g to 19c. During this process,
        %    we also downgraded from Enterprise Edition to Standard Edition.}
        \item {Worked on upgrading the private procurement application from Java 6 to Java 8 and tomcat version 5.5 to version 8.5}
        \item {Worked on moving both of the application's on-premise Jenkins builds and deployments to run in the cloud version of Azure DevOps pipelines.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Software Engineer} % Job title
    {Progeny Systems} % Organization
    {Manassas, VA} % Location
    {September '15 til February '17} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on multiple web applications that dealt with NLP and transforming free text into Medical Codes}
        \item {Worked on an application that would take oracle .dmp files of analytical data from a submarine,
            compress it, and burn it to a Disk or transmit it wirelessly. It would also be running in the lab 
            and perform the decompression of the data so that it could be used to analyze the submarine's systems while out at sea.}
        \end{cvitems}
    }
\end{cventries}
